Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-24 doc/main_jfm.tex
re-calculated table 1

Table~\ref{table1} provides dimensional friction coefficients $b$ for several shear rates
and the results are in quantitative agreement with 
values previously reported in the literature~\cite{sch-vla-mik2010} and~\cite{denOtter2007}.  
The coefficients generally lie within the range 1 to 2 pN$\cdot$ns nm$^{-2}$ but there are some 
outliers.  These outliers ($\dot\gamma = 0.0025$ ns$^{-1}$ and 
$\dot\gamma = 0.0040$ ns$^{-1}$) correspond to slip velocities that are too low relative to shear rate (see the green and red curve in Figure \ref{figure5}: panel (c)).
The JP vesicle consists of only  58 particles and so it is not surprising that discrete effects produce outliers.

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c c c c c }
 $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
\hline                    
$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
$b$ (pN$\cdot$ns nm$^{-2}$)    & 1.38 &  5.43 & 1.37 &  1.33 & 8.07 & 1.94  & 1.89\\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}

>>>>

Table~\ref{table1} provides dimensional friction coefficients $b$ for several shear rates
and the results are in quantitative agreement with 
values previously reported in the literature~\cite{sch-vla-mik2010} and~\cite{denOtter2007}.  
The coefficients generally lie within the range 1 to 2 pN$\cdot$ns nm$^{-2}$ but there are some 
outliers.  These outliers ($\dot\gamma = 0.0041$ ns$^{-1}$ and 
$\dot\gamma = 0.0066$ ns$^{-1}$) correspond to slip velocities that are too low relative to shear rate (see the green and red curve in Figure \ref{figure5}: panel (c)).
The JP vesicle consists of only  58 particles and so it is not surprising that discrete effects produce outliers.

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c c c c c }
 $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
\hline                    
$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87  & 0.22 &0.21 & 1.29 & 0.31 & 0.30\\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}
